Wikipedia WALS Feature Analysis

### 2019-07-10 surprisal/WALS_features.Rmd
working on imputation of common languages

```{r }
wkpd <- read.csv(here("Data/wikipedia_unigrams.csv"))
LANGUAGES <- wkpd$language

@@

```{r comparison: features to cosines}
#imputed_df <- 
  common_df %>% 
  gather(feature, value, -language) %>%
  group_by(feature) %>%
  mutate(value = factor(value)) %>%
  select(language, feature, value) %>%
  ungroup() %>% 
  spread(feature, value) %>% 
  sapply(as.factor) %>%
  as.data.frame() %>%
  column_to_rownames("language") %>% pull(X98A) %>% length()
  MIMCA(ncp = 1)

@@

feature_names <- read_feather(here("Wikipedia/feature_names.feather"))

>>>>

```{r read in data}
wkpd <- read.csv(here("Data/wikipedia_unigrams.csv"))
LANGUAGES <- wkpd$language

@@

```{r comparison: features to cosines}
imputed_df <- common_df %>% 
  gather(feature, value, -language) %>%
  group_by(feature) %>%
  mutate(value = factor(value)) %>%
  select(language, feature, value) %>%
  ungroup() %>% 
  spread(feature, value) %>% 
  sapply(as.factor) %>%
  as.data.frame() %>%
  column_to_rownames("language") %>% dim()
  MIMCA(ncp = 1)

@@
